---
title: "Group Assignment 07"
format: html
editor: visual
author: "Emily Möller (s251702), Erine Genilloud (s252025), Mazarine Chambon (s251918), Yann Ducrest (s251889), Hedi Khemakhem (s251900)"
---

## Load libraries

```{r}
#| echo: false
library("tidyverse")
library(broom)
```

## Load data

```{r}
#| echo: false
biopsy <- read_csv("https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
```

## Emily

```{r}
head(biopsy)
```

Clump Thickness vs Bare Nuclei by Outcome

```{r}

ggplot(biopsy, aes(x = clump_thickness, y = bare_nuclei, color = outcome)) +
  geom_point(alpha = 0.7, size = 3) +
  labs(
    title = "Clump Thickness vs Bare Nuclei by Outcome",
    x = "Clump Thickness",
    y = "Bare Nuclei"
  )
```

## Yann

```{r}
biopsy |>
  select(where(is.numeric)) |>
  prcomp(scale = TRUE) |>
  augment(biopsy) |>
  ggplot(aes(.fittedPC1, .fittedPC2, color = outcome)) +
  geom_point(size = 2) +
  theme_minimal()

```

## Hedi

```{r}
library(broom)  # devtools::install_github("tidymodels/broom")
library(cowplot)
```

```{r}
ggplot(biopsy, aes(x = outcome, y = clump_thickness, fill = outcome)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Clump Thickness by Outcome",
    x = "Outcome",
    y = "Clump Thickness"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

Boxplot representing the difference of clump thickness between malignant and benign cells.\
Malignant samples show thicker and more variable cell clumps, while benign ones stay lower and more consistent — a pattern typical of cancerous tissue.

## Erine

```{r}
biopsy |> 
  ggplot(aes(x = clump_thickness, y=uniform_cell_size)) +
  geom_point(aes(color = outcome)) +
  labs(
    x = "Clump thickness",
    y = "Uniform cell size",
    title = "Clump thickness by cell size"
  )
```

In this graph, we can see that there is a correlation between clump thickness and the state of the cell.

For example, a cell of size 3 has a high probability of being malignant if the clump thickness is higher than 7.

## Mazarine

```{r}
ggplot(biopsy, aes(x = clump_thickness, y = epithelial_cell_size, color = outcome)) +
  geom_point(alpha = 0.7, size = 3) +
  labs(
    title = "Clump Thickness vs Epithelial Cell Size by Outcome",
    x = "Clump Thickness",
    y = "Epithelial Celle Size"
  )
```
